---
title: "topdown"
author:
- name: Sebastian Gibb
  affiliation: Department of Anesthesiology and Intensive Care, University Medicine Greifswald, Germany.
- name: Pavel V. Shliaha
  affiliation: Department of Biochemistry and Molecular Biology, University of Southern Denmark, Denmark.
package: topdown
abstract: >
  This vignette describes the setup and basic functionality
  of the 'topdown' package.
output:
  BiocStyle::html_document2:
    toc_float: true
    tidy: TRUE
vignette: >
  %\VignetteIndexEntry{TopDown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteKeywords{Mass Spectrometry, Proteomics, Bioinformatics}
  %\VignetteEncoding{UTF-8}
  %\VignettePackage{topdown}
---

```{r environment, echo=FALSE}
suppressPackageStartupMessages(library("topdown"))
suppressPackageStartupMessages(library("BiocStyle"))
```

```{r include_forword, child="Foreword.md"}
```

```{r include_bugs, child="Bugs.md"}
```

# Introduction

# Setup the *Thermo Software*

1. Install the workstation by running `OrbitrapFusionLumosWorkstation.exe`.
2. Run `C:\Thermo\Instruments\TNG\OrbitrapFusionLumos\2.1\System\programs\TNGInstrumentConfigControl.exe`,
   set *Optional Ion Source* to *ETD and Internal Calibration*, click *Apply* and *OK* (you could ignore the *restart your instrument* message).
3. Replace `C:\Thermo\Instruments\TNG\OrbitrapFusionLumos\2.1\System\programs\Thermo.TNG.Calcium.MethodXML.dll` by `Thermo.TNG.Calcium.MethodXML.dll`.

```{r sessioninfo}
sessionInfo()
```

# References
