---
title: "topdown"
author:
- name: Sebastian Gibb
  affiliation: Department of Anesthesiology and Intensive Care, University Medicine Greifswald, Germany.
- name: Pavel V. Shliaha
  affiliation: Department of Biochemistry and Molecular Biology, University of Southern Denmark, Denmark.
package: topdown
abstract: >
  This vignette describes the setup and basic functionality
  of the 'topdown' package.
output:
  BiocStyle::html_document2:
    toc_float: true
    tidy: TRUE
vignette: >
  %\VignetteIndexEntry{TopDown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteKeywords{Mass Spectrometry, Proteomics, Bioinformatics}
  %\VignetteEncoding{UTF-8}
  %\VignettePackage{topdown}
---

```{r environment, echo=FALSE}
suppressPackageStartupMessages(library("topdown"))
suppressPackageStartupMessages(library("BiocStyle"))
```

```{r include_forword, child="Foreword.md"}
```

```{r include_bugs, child="Bugs.md"}
```

# Introduction

# Setup

## Setup the Thermo Software

1. Install the workstation by running `OrbitrapFusionLumosWorkstation.exe`.
2. Run `C:\Thermo\Instruments\TNG\OrbitrapFusionLumos\2.1\System\programs\TNGInstrumentConfigControl.exe`,
   set *Optional Ion Source* to *ETD and Internal Calibration*, click *Apply* and *OK* (you could ignore the *restart your instrument* message).
3. Replace `C:\Thermo\Instruments\TNG\OrbitrapFusionLumos\2.1\System\programs\Thermo.TNG.Calcium.MethodXML.dll` by `Thermo.TNG.Calcium.MethodXML.dll`.

## Setup XMLMethodChanger

**TODO:**: has to be easier and more user-friendly:
Download and compile https://github.com/thermofisherlsms/meth-modifications

## Setup Operating System

In order to use `XMLMethodChanger` the operating system has to use the `.` (dot)
as decimal mark and the `,` (comma) as digit group separator (one thousand dot
two should be formated as `1,000.2`).

In *Windows 7* the settings are located at `Windows Control Panel > Region and Language > Formats`.
Choose *English (USA)* here or use the *Additional settings* button to change it
manually.

## Setup ScanHeadsman

Download *ScanHeadsman* from https://bitbucket.org/caetera/scanheadsman

It requires Microsoft **.NET 4.5** or later (it is often preinstalled on a typical modern Windows
or could be found in Microsoft's Download Center, e.g.
https://www.microsoft.com/en-us/download/details.aspx?id=30653).
Additionally you would need Thermo's *MS File Reader* which could be downloaded
free of charge (but you have to register) from the Thermo FlexNet website:
https://thermo.flexnetoperations.com/

```{r sessioninfo}
sessionInfo()
```

# References
